InteroceptionStudy_GPValidation

### 2021-08-31 IAPS_PREPROCESSING_2021_1.Rmd
fixed ssid 352 and 353
fixed an issue where artifact digital signals were sent as stim, resulting in an error that mad it hard to create trial numbers on the fly during pre-pocessing. 352 had an extra trial 70 and 353 had a trigger 99 which didn't actually exist in the data

unique(db_HR_bionew$filename)

@@

# this will delete fixation and stuff so no
# db_HR_bio1<- subset(db_HR_bio,db_HR_bio$trigger2< 100)

@@

# use this

db_HR_bio1no328<-subset(db_HR_bio1, db_HR_bio1$ssid!= 328)

@@

db_HR_bio1no328<- db_HR_bio1no328%>%
  arrange(as.numeric(timestart), ssid)

@@

```{r}
db_HR_bio2<- db_HR_bio328 %>%
  group_by(ssid)%>%
  mutate(tNo = -6:(n()-7))
unique(db_HR_bio328$tNo)
```

```{r}
db_HR_bio2<- bind_rows(db_HR_bio1no328,db_HR_bio328)
db_HR_bio2<-db_HR_bio1no328

@@

db_HR_bio2<- select(db_HR_bio2, c(timestart,Mean_HR, tNo, ssid))

str((db_HR_bio2))
# str(db_biohrold2)
db_biohr$tNo<- db_biohr$tno
db_biohrold2<- db_biohr

@@

db_biohrold2$timestart<- as.numeric(db_biohrold2$timestart)

db_HR_bio2$Mean_HR<- as.numeric(db_HR_bio2$Mean_HR)
db_biohrold2$Mean_HR<- as.numeric(db_biohrold2$Mean_HR)

db_HR_bio2$tNo<- as.character(db_HR_bio2$tNo)
db_biohrold2$tNo<- as.character(db_biohrold2$tNo)
db_HR_bio2$ssid<- as.character(db_HR_bio2$ssid)

@@

db_HR_bio2<- db_HR_bio2[,1:4]

db_HR_bio2$Mean_HR<- as.numeric(db_HR_bio2$Mean_HR)

@@

# final
db_HR_bio_final<- db_HR_bio2
db_HR_bio_final<- bind_rows(db_HR_bio2, db_biohrold2test)

@@

write_csv(db_HR_bio_final, 'db_HR_bio_final_346_355.csv')

>>>>

unique(db_HR_bionew$filename)
nrow(db_HR_bionew)

@@

# this will delete fixation and stuff so no
db_HR_bio1<- subset(db_HR_bio,db_HR_bio$trigger2> 15)

@@

# use this
table(db_HR_bio1$ssid!= 328)
db_HR_bio1no328<-subset(db_HR_bio1, db_HR_bio1$ssid!= 328)

@@

db_HR_bio1no328<- db_HR_bio1no328%>%
  arrange(ssid,as.numeric(timestart))

@@

```{r}
# db_HR_bio2<-

unique(db_HR_bio1no328$stim)
db_HR_bio1no328<- db_HR_bio1no328 %>%
  group_by(ssid)%>%
  mutate(tNo = -6:(n()-7))

unique(db_HR_bio1no328$tNo)
```

```{r}
View(db_HR_bio1no328)

unique(db_HR_bio1no328$ssid)
unique(db_HR_bio328$ssid)
# db_HR_bio2<- bind_rows(db_HR_bio1no328,db_HR_bio328)
db_HR_bio2<-db_HR_bio1no328

@@

colnames(db_HR_bio2)
db_HR_bio2<- select(db_HR_bio2, c(timestart,Mean_HR, tNo, ssid,trigger2,trigger_200, trigger,stim,mhrtext))

# store only fixation screens

# create screecontr.treatment()
unique(db_HR_bio2$trigger)
unique(db_HR_bio2$trigger2)

db_HR_bio2$screen_content<- if_else(db_HR_bio2$trigger == 100, "Rest",
                                    if_else(db_HR_bio2$trigger == 101, "fixation",
                                    if_else(db_HR_bio2$trigger == 102, "valence",
                                    if_else(db_HR_bio2$trigger == 103, "arousal",
                                    "stim"))))

unique(db_HR_bio2$trigger)

db_HR_bio2$timestart<- as.numeric(db_HR_bio2$timestart)
db_HR_bio2.1<- db_HR_bio2 %>%
  group_by(ssid)%>%
  arrange(ssid, timestart)%>%
  group_by(ssid,screen_content)%>%
  # arrange(ssid, timestart)%>%
  mutate(tNo =  1:n())
   arrange(timestart,ssid)
  # subset(trigger == 100)

unique(db_HR_bio2.1$tNo)

unique(db_HR_bio2.1$tNo-8)
table(db_HR_bio2.1$tNo)

db_HR_bio2.1$tNo2<- if_else(db_HR_bio2.1$screen_content == "Rest", -7,
                           as.numeric(as.character(db_HR_bio2.1$tNo)))

db_HR_bio2.1$tNo3<- if_else(db_HR_bio2.1$tNo2 >0 &  db_HR_bio2.1$tNo2< 7, db_HR_bio2.1$tNo2-7,
                          if_else(db_HR_bio2.1$tNo2  >6, db_HR_bio2.1$tNo2-6, db_HR_bio2.1$tNo2))

table(db_HR_bio2.1$tNo3)
test352<- subset(db_HR_bio2.1, ssid == 352)
test353<- subset(db_HR_bio2.1, ssid == 353)
table(test352$tNo3)

write_csv(test352, "test352.csv")

# fixed the issue was trial 15 is supposed to be trigger 23 but we also had a 70, that can be seen on the psychopy data files
write_csv(test353, "test353.csv")

# on 353 the issue was a 99 trigger bveing loaded as a stim

# export 352 and 353 and corect manually, they seems ot have an extra trigger

db_352 <- read_csv("352_Biohr_fixed.csv")
db_353 <- read_csv("353_Biohr_fixed.csv")
unique(db_352$ssid)
db_352
nrow(db_353)

# new dataset withouth the problem ssids
db_HR_bio2.2<- subset(db_HR_bio2.1, ssid != "352")
db_HR_bio2.2<- subset(db_HR_bio2.2, ssid != "353")

nrow(db_HR_bio2.2)

unique(db_HR_bio2.2$ssid)

db_352_353<- bind_rows(db_352, db_353)

nrow(db_352_353)

db_HR_bio2.2$ssid<- as.character(db_HR_bio2.2$ssid)
db_352_353$ssid<- as.character(db_352_353$ssid)

db_352_353$trigger <- as.character(db_352_353$trigger)

nrow(db_HR_bio2.2)
# nrow(db_HR_bio2.1) 2021 result should be less than this

nrow(db_352_353)

db_HR_bio2.3<- bind_rows(db_HR_bio2.2,db_352_353)
nrow(db_HR_bio2.3)
# order

db_HR_bio2.3.1<- db_HR_bio2.3 %>%
  group_by(ssid)%>%
  arrange(ssid, timestart) %>%
  group_by(ssid,screen_content)%>%
  # arrange(ssid, timestart)%>%
  mutate(tNo =  1:n())
   # arrange(timestart,ssid)
  # subset(ssid == 353)

table(db_HR_bio2.3.1$tNo)

# test<- subset(db_HR_bio2.3.1, ssid == "353")

unique(db_HR_bio2.3.1$tNo)

db_HR_bio2.3.1$tNo2<- if_else(db_HR_bio2.3.1$screen_content == "Rest", -7,
                           as.numeric(as.character(db_HR_bio2.3.1$tNo)))

db_HR_bio2.3.1$tNo3<- if_else(db_HR_bio2.3.1$tNo2 >0 &  db_HR_bio2.3.1$tNo2< 7, db_HR_bio2.3.1$tNo2-7,
                          if_else(db_HR_bio2.3.1$tNo2  >6, db_HR_bio2.3.1$tNo2-6, db_HR_bio2.3.1$tNo2))

unique(db_HR_bio2.3.1$tNo3)
```

```{r}
unique(db_HR_bio2.3.1$screen_content)
table(is.na(db_HR_bio2.3.1$screen_content))

str((db_HR_bio2.3.1))
# str(db_biohrold2)
db_biohr$tNo<- db_biohr$tno
db_biohrold2<- db_biohr

@@

View(db_biohrold2)
db_biohrold2$timestart<- as.numeric(db_biohrold2$timestart)

# View(db_HR_bio2)
db_HR_bio2$Mean_HR<- as.numeric(db_HR_bio2$Mean_HR)
# db_biohrold2$Mean_HR<- as.numeric(db_biohrold2$Mean_HR)

db_HR_bio2$tNo<- as.character(db_HR_bio2$tNo)

db_biohrold2$tNo<- as.character(db_biohrold2$tNo)
db_HR_bio2$ssid<- as.character(db_HR_bio2$ssid)

@@

db_HR_bio2<- db_HR_bio2[,1:4]
db_HR_bio2$Mean_HR<- as.numeric(db_HR_bio2$Mean_HR)

@@

# final
colnames(db_HR_bio_final)
db_HR_bio2.3.1
colnames(db_HR_bio2.3.1)

unique(db_HR_bio2.3.1$tNo)
db_HR_bio2.3.1
db_HR_bio2.3.2<-select()
db_HR_bio_final<- select(db_HR_bio2.3.1, c(1,12))

# db_HR_bio_final<- bind_rows(db_HR_bio2, db_biohrold2test)

View(db_HR_bio_final)

@@

write_csv(db_HR_bio_final, 'db_HR_bio_final_346_355_withfix.csv')
